\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-08 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Evaluating the Impact of Offline Store Clusters under the Consolidation: Evidence from China's Metropolitan Real Estate Market \footnote{
The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China. We are grateful for the comments and suggestions made at the meeting. The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (2019hhf-08; SKSYL201812; 2018jj-01) and National Natural Science Foundation of China (71773081). % We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.
}}

@@

% Police brutality, law enforcement, and crime: Evidence from Chicago
\begin{abstract}
    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, in the context of online platform development. By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the study explores how the strategic clustering of offline stores enhances Lianjia's influence in local communities and facilitates the creation of an extensive franchise network. This study first conducts a regression discontinuity (RD) design to quantify the optimal influence radius of these stores on housing transactions. By incorporating the optimal influence radius, this study examines the exogenous shock of Lianjia's market entry to identify a significant increase in transaction revenues. However, this effect is diminished during Covid-19 periods. In addition, the paper examines the impact of Lianjia's ACN strategy on its platformization efforts and concludes that the effect is not only from the larger client base brought by the platform, but also from the information control by sharing information within the platform. This study provides valuable insights into the synergy between offline store expansion and online platform development, highlighting their importance in the evolving real estate brokerage market.
  \end{abstract}

@@

% Brokerage consolidation refers to the process by which a larger real estate brokerage firm integrates multiple smaller brokerage firms into a single, unified platform.

In the real estate market, transaction cost is a critical factor for both buyers and sellers. Minimizing these costs has made the selection of competent real estate agencies a significant priority for both parties. Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communication channel between buyers and sellers \citep{glaeser_real_2017}. In addition, technological advancements coupled with the proliferation of dominant platforms have created a trend toward greater monopolization within the real estate brokerage industry, rather than fostering a competitive environment. Therefore, it is imperative to analytically examine the expansion strategies of Chinese real estate agencies, especially in the context of escalating platform-based monopolization.

Lianjia is the largest real estate brokerage in China that has platformed real estate transactions by establishing the Beke platform. They can expand rapidly by the expansion of offline stores on a large scale while sharing resources by leveraging the advantages of their platform. Beke has also established an original Agent Cooperate Network (ACN) that integrates and shares the content of its multiple subsidiaries to realize multiple revenue models at the same time.\footnote{The ACN model breaks down the entire process of transaction into parts, each of which is handled by a single person or store, including seller-side: finding sellers, maintaining the listing of the house, commissioning and communicating, and buyer-side: Finding clients, matching homes and clients, facilitating transactions, and providing financial services assistance.} Through the ACN model, Lianjia transforms the internal competition within the system into the overall competitiveness of the system, improving the reputation and influence of the entire brand and gaining a more favorable position in the marketplace. For example, according to the data of AutoNavi Map and CREIS data: In 2020, the number of real estate agent stores in the main urban area of Chengdu City that accessed Beke Housing's platform accounted for about 20\%, but the market share reached 73.98\%.

The reason why Lianjia does not have such a high proportion of offline stores in the market but has an absolute dominant position in metropolis can be explained by the mechanism of China's second-hand real estate market. In the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction. However, due to the asymmetric information characteristics of the real estate market, sellers must find a way to inform buyers and match buyers. In a fully competitive market, sellers would be indifferent in choosing real estate agents. Nevertheless, as the market trends towards increased monopolization, sellers encounter a dichotomous choice: opt for a larger brokerage firm, which, albeit commanding higher fees, possesses the capacity to expedite housing transactions, or engage with a smaller brokerage, which presents a contrasting scenario of lower fees yet potentially less efficient transaction facilitation.

While it is possible for sellers to adopt a multi-homing strategy, this approach is suboptimal for several reasons. First, the exclusivity of contracts between sellers and agents precludes the adoption of a multi-homing strategy. Second, although sellers can list their houses with multiple brokerages, smaller brokerages often lack a broad enough target client base, which is not very helpful in selling the homes. Third, connecting with multiple brokers simultaneously can make each brokers feel that they are in a difficult position to compete for that house, which reduces their incentive to be proactive in their efforts. Finally, while the variance in service costs between agencies is acknowledged, these costs are trivial compared to the value of the property and are more related to the risk associated with holding a financial asset. Consequently, risk-averse individuals are inclined to choose an agency that provides a guaranteed level of service. Due to the mechanism of online promotion and offline transaction in the real estate brokerage industry, the nature of the brokerage's services in the offline stores is of high value for its influence on the client side. This is the principle behind Lianjia's choice to open stores in the neighborhoods of each target community. By opening a wide range of stores around the communities, the brokerage attracts sellers to list their houses, and attracts buyers in the market through its extensive platform sources, thus obtaining a higher number of transaction and income from the transaction.

In this paper, we empirically test this hypothesis that when brokerages are able to expand their offline stores' coverage in the communities, the brokerages can earn higher income in this community, and we decompose the channels into two parts. On the one hand, is that when brokers have better control over listing information by opening additional offline stores, they are more likely to attract more sellers to choose them, which will then benefited by the online platform effect to extract more buyers and more likely to complete a transaction. On the other hand, when offline stores are closer to the communities, they are more likely to make a house tour to help the buyers to get more information on the house, and therefore, be more likely to complete a transaction. During the Covid-19 pandemic period, the Chinese government restricts the number, and in this period, we find that the number of houses tour is not significantly affected by the number of offline stores, but the listing information significantly decreases because the brokerages are difficult to interact with the sellers and then failure to maintain the information advantage during this period.

>>>>

\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Offline Store Expansion and Platform Consolidation: Evidence from major cities in China \footnote{
The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China. We are grateful for the comments and suggestions made at the meeting. The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (2019hhf-08; SKSYL201812; 2018jj-01) and National Natural Science Foundation of China (71773081). % We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.
}}

@@

% Police brutality, law enforcement, and crime: Evidence from Chicago
\begin{abstract}
    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, within the framework of platform consolidation. By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the research investigates how the transaction patterns of traditional brokerages, characterized by strategic clustering of offline stores, transition towards online consolidation, thereby facilitating the development of an extensive franchise network. Utilizing a regression discontinuity (RD) design, the study quantifies the optimal influence radius of these stores on housing transactions. Incorporating this optimal influence radius, the study further investigates the exogenous shock of Lianjia's market entry, identifying a significant increase in transaction revenues before the Covid-19. However, this effect is attenuated during the Covid-19 period due to remote work and other restrictive policies implemented by the Chinese government. Additionally, the paper explores the impact of Lianjia's Agent Cooperation Network (ACN) strategy on its platform consolidation effect, concluding that this strategy enhances Lianjia's revenue generation and facilitates transactions. This study provides valuable insights into the synergy between offline store expansion and online platform development, highlighting future trajectories in the evolving real estate brokerage market.
  \end{abstract}

@@

In the real estate market, transaction cost is a critical factor for both buyers and sellers. Minimizing these costs has made the selection of competent real estate agencies a significant priority for both parties. Real estate brokers not only help in reducing transaction costs but also provide essential market information, negotiation support, and legal assistance, thereby ensuring smoother and more efficient transactions. Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communication channel between buyers and sellers \citep{glaeser_real_2017}. Their expertise and local market knowledge have become indispensable in navigating the complex real estate landscape.

The Chinese real estate brokerage market has long been characterized by intense competition among offline stores, with multiple brokerages establishing a presence within the same community to vie for clients. However, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions. Brokerage consolidation, a process where larger firms absorb smaller ones into a unified platform, is emerging as a transformative trend, redefining how properties are bought and sold across China.

Lianjia, the largest real estate brokerage in China, has revolutionized real estate transactions through the establishment of the Beke platform. This platform enables rapid expansion by integrating offline stores on a large scale while leveraging the advantages of resource sharing. However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market. However, in 2018, Beke established a new strategy named Agent Cooperate Network (ACN), which integrates and shares the content across its multiple subsidiaries to realize multiple revenue models simultaneously.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores. These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.}

Through the ACN model, Lianjia transforms internal competition within the system into overall system competitiveness, thereby enhancing the brand's reputation and market influence. More importantly, this strategic allows Lianjia to cooperate with other previously competitors by consolidating resources and forms a consolidation. For instance, data from AutoNavi Map and CREIS indicate that in 2020, although only about 20\% of real estate agent stores in the main urban area of Chengdu City are Lianjia's offline stores, these stores achieved a market share of 73.98\%. This remarkable market penetration underscores the efficacy of Beke's integrated platform and ACN model in dominating the real estate brokerage landscape. The Table \ref{tab:precise_proportion_contraction} shows the comparision of the market share of Lianjia and the share of the number of stores in the market.

What's more, in the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction. However, due to the asymmetric information inherent in the real estate market, sellers face challenges in effectively informing and matching with potential buyers. n a perfectly competitive market, sellers would be indifferent in their choice of real estate agents. Nonetheless, as the market trends toward increased monopolization, sellers confront a dichotomous decision: engage a larger brokerage firm, which, despite higher fees, offers the potential for expedited transactions, or opt for a smaller brokerage with lower fees but potentially less efficient transaction facilitation.

While sellers may consider a multi-homing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons. Firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a multi-homing strategy. Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes.Thirdly, engaging multiple brokers simultaneously can lead to reduced incentives among agents, as they perceive competition for the same property, diminishing their proactive efforts. Finally, while service cost variations between agencies are acknowledged, these costs are minor compared to the property's value and are more closely related to the risks associated with holding a financial asset. Consequently, risk-averse sellers are inclined to choose an agency that provides a guaranteed level of service.

Given the dual nature of online promotion and offline transactions in the real estate brokerage industry, the quality of offline services is crucial for influencing client decisions. This principle underpins Lianjia's strategy of establishing numerous stores within targeted communities. By opening a wide range of stores in various neighborhoods and adopting a downstream consolidation model through platform design, the brokerage effectively attracts sellers to list their properties and buyers through its extensive platform resources. This strategy not only enhances transaction volume but also increases income derived from these transactions.

In this paper, we empirically estimate the offline stores' , the brokerages can earn higher income in this community, and we decompose the channels into two parts. On the one hand, is that when brokers have better control over listing information by opening additional offline stores, they are more likely to attract more sellers to choose them, which will then benefited by the online platform effect to extract more buyers and more likely to complete a transaction. On the other hand, when offline stores are closer to the communities, they are more likely to make a house tour to help the buyers to get more information on the house, and therefore, be more likely to complete a transaction. During the Covid-19 pandemic period, the Chinese government restricts the number, and in this period, we find that the number of houses tour is not significantly affected by the number of offline stores, but the listing information significantly decreases because the brokerages are difficult to interact with the sellers and then failure to maintain the information advantage during this period.
